Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-11-29 documents/ms/ms.tex
PASP main script

\usepackage{graphicx}
\usepackage{caption} 
\usepackage{subcaption} 
\usepackage{color}
\usepackage{hyperref}
\usepackage{url}

@@

\graphicspath{{figures/png/}}

\newcommand{\notenglish}[1]{\textit{#1}}
\newcommand{\sic}{\notenglish{sic}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Kepler}{\project{Kepler}}
\newcommand{\name}{CPM}
\newcommand{\set}[1]{\mathcal{#1}}
\newcommand{\given}{\,|\,}
\newcommand{\todo}[1]{\textbf{#1}}

@@

\title{
  Calibrating the pixel-level Kepler imaging data with a causal data-driven model
 \\ 
}
\author{%
  Dun~Wang\altaffilmark{\ref{CCPP}},
  Dan~Foreman-Mackey\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}}
  }
\newcounter{address}
\setcounter{address}{1}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CCPP}%
  Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CDS}%
  Center for Data Science, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
  Max-Planck-Institut f\"ur Astronomie, Heidelberg, Germany}
\altaffiltext{\theaddress}{\stepcounter{address}\label{email}%
  To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
  Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
the most precise photometric measurements of stars ever made---%
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level so that
it can capture very fine-grained information about the variation of the spacecraft.
The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star. In addition, we use the target star's future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components), which we set by cross-validation. 
We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.

@@

\section{Ultra-precise photometry}

The photometric measurements of stars made by the \Kepler\ Satellite are precise enough
  to permit discovery of exoplanet transits with depths smaller than $10^{-4}$.
This precision results from great spacecraft stability,
  supplemented by various methods for removing small residual spacecraft-induced and stellar-variability trends in the brightnesses,
  either filtering the data (with things like median filters; \cite{trendfilter})
  or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; 
  \cite{gaussian}).
When employed in the service of exoplanet search and characterization,
  these methods are usually agnostic about whether photometric variations originate in the spacecraft or in the star itself;
  that is, they obliterate intrinsic stellar variability along with spacecraft issues.

In general, there are many reasons for apparent photometric variability in a \Kepler\ source.
There is intrinsic stellar variability,
  which is of interest to some and a nuisance to others.
There is also variability of overlapping fainter stars;
  that is, confusion noise combined with variability of the confusing sources.
There are small changes in spacecraft pointing,
  which leads to slightly different illumination of the focal-plane pixels,
  and thus different sensitivity to variations in the device.
There are also \emph{intra-pixel} sensitivity variations that can contribute \citep{whitepaper}.
There are small changes in spacecraft temperature,
  which lead to point-spread function (PSF) and differential (across the focal plane) pointing changes.
These also lead to changes in pixel and intra-pixel illumination.
Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
There is electronic cross-talk between detectors and charge-transfer inefficiency;
  these can effectively transfer variability from one source to another.
There are additional electronics effects like ``rolling bands'' that put additional features into light-curves.
There are also probably changes to the detector sensitivity with temperature and time,
  possibly illimunation-history effects,
  and possibly sources of variability not yet considered.
The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
  much higher than ever previously attempted;
  new effects really \emph{must} appear at some point.
In \figurename~\ref{ccd}, we show the pixel-level variability in the \Kepler\ data
  near one bright star that shows minimal intrinsic variability;
  this figure highlights the spacecraft-induced effects.

We propose and advise dealing with these variations in \Kepler\ light-curves by \emph{modeling} them.
In this context, a model is (at least) a parameterized function that can predict data, given parameter settings,
  and an objective function that can be used to set or sample those parameters.
In some cases, the objective function can be given a probabilistic justification or interpretation, e.g., if it is constructed using a likelihood and a prior pdf.
The model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
  or it can be a flexible, effective model that has no direct interpretation in terms of physical spacecraft parameters.
If done well, we would expect a physical model to do a better job,
  because it embodies more prior information,
  but it requires research and intuition about dominant effects. 
If this research and intuition is wrong or incomplete, a physical model may actually perform worse.
The model we propose here is in the non-physical, effective category.
The \Kepler\ community is familiar with these kinds of models;
  to our knowledge, \emph{all} successful light-curve ``de-trending'' methods
  are flexible, effective models.

One such method---one that is designed to describe or model spacecraft-induced problems
  but \emph{not} interfere with measurements of stellar variability---%
  is the \Kepler\ Presearch (\sic) Data Conditioning (PDC, \cite{pdc1}).
The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities. 
%This seems the original paper on PDC:
%[PDC1] https://kepler.nasa.gov/science/ForScientists/papersAndDocumentation/SOCpapers/7740-67-pdc-jtwicken-copyright.pdf
%
%This describes the later version of PDC:
%[PDC2] http://arxiv.org/pdf/1203.1382v1.pdf
%[PDC3] http://arxiv.org/pdf/1203.1383v1.pdf

In the first PDC \citep{pdc1}, 
  removal of systematic errors was performed based on correlations with a set of ancillary engineering data. 
These data include the temperatures at the local detector electronics below the CCD array, 
  and polynomials describing the centroid motion of the targets from PA.

In \cite{pdc2,pdc3}, filtered light-curves of other stars are used instead. 
The light-curve of a target star is projected on the leading eight principal components of these light-curves. 
This projection is then removed from the star's light-curve. 
The principal components are computed from a set of relatively quiet stars close in position and magnitude. 
This was done since it was observed that otherwise, too much of the stellar variability was being removed.

From the point of view of the present paper, 
one can only guarantee that {\em no} stellar variability is removed if the stars do not depend on time at all. 
If both the target star signal as well as some of the other stars do depend on time, 
  then time acts as a confounder influencing both, and thus the true signals are not statistically independent, 
  and thus the target signal may be compromised. 
We suspect that this effect is limited in \cite{pdc2,pdc3}, 
  since only eight principal components are used, which limits the capacity of the model.

PDC ``de-trends'' the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
  generated from a principal components analysis (PCA) of filtered light-curves.
That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
  by filtering and restricting the dimensionality (through PCA).

The method proposed here, \name, shares the motivation of PDC.
The main differences are that
\begin{enumerate}
\item
\name\ works in the pixel domain, not the light-curve domain, so it has access to more fine-grained information
\item
\name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the light-curves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework.
\item 
\name\ directly optimizes for prediction accuracy, while PDC uses PCA projections.
\item
the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
  variability is also removed as well as the systematics.
\item 
\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light-curves) of the other stars.
\end{enumerate}

The two methods (\name\ and PDC) are similar however,
  in that they both make the (implicit or explicit) assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
  must also be imprinting similar or related variability on other light-curves.
In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).
By going to the pixel level (unlike the PDC, which works at the photometry level),
  \name\ makes it easier for the model to capture variability
  that is coming through variations in the centroids and point-spread function
  from spacecraft pointing, roll, and temperature.

Before we start, a few reminders about the \Kepler\ data are in order:
The satellite always observes precisely the same field, at fixed pointing (as closely as possible).
Only a few percent of the 80 million pixels in the focal plane are telemetered down
  to Earth from each 30-min exposure;
  the telemetered pixels are associated with \Kepler\ target stars chosen for study by the \Kepler\ Team.
The satellite is rolled by 90~deg every 90-ish days (to satisfy Solar-Angle constraints).
The focal plane contains many CCDs;
  this plus the 90-deg rotations means that each star is at a particular location
  on a particular CCD for 90-ish-day contiguous periods of time.
The PSF varies strongly across the field and is badly sampled.
The stars span a huge range in brightness;
  some of \Kepler's most important targets even saturate the device and bleed charge.
The stellar photometry returned by the \Kepler\ SAP and PDC pipelines is based on
  straight, \emph{unweighted} sums of pixels in small patches centered on the stellar centroid.
We will return to this latter point at the end;
  this kind of photometry cannot be optimal;
  it must be possible to do a better job with the photometric measurements.
That's beyond the scope of this project but a place for a valuable intervention on the \Kepler\ data.

The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.

We describe the method and deliver all the relevant code in a public, open-source repository.
We also provide an interface to the \Kepler\ data that delivers improved ``\name\ photometry''
  for every \Kepler\ target.

@@

The second general idea about data-driven modelling is the investigator's beliefs
  about the causal processes that generate the data
  are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data
  and the data-taking system
  lead to different structures for the data-driven model.
In the case of \Kepler\ data, 
  if we examine two arbitrary stars far away from each other 
  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light-curve time series), 
  we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
  If we believe that different stars in the \Kepler\ field vary independently 
  (that is, are not physically synchronized in any way) because of the distance between them, 
  then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels
  inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause---the systematics.  
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't contain information about
  the signals of interest (i.e., the transits).
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the 
  target star.
In what follows, we are going to use input data both from pixels of other stars and the  
target star pixels' past and future.
These models ought to remove both spacecraft variability and intrinsic stellar variability, 
which is optimal for exoplanet transit searching.

\begin{figure}[htb]
\centering
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5088536-5}
\caption{}
\end{subfigure}%
\hfill
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5949551-5}
\caption{}
\end{subfigure}
\caption{
  \label{ccd} 
  Stars on the same CCD share systematic errors. 
  The two panels show pixel fluxes (brightnesses) for two stars in quarter 5: (a) KIC 5088536, (b) KIC 5949551; 
  here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
  but far enough apart such that there is no stray light from one affecting the other. 
  Each panel shows the pixels contributing to the respective star.
  Note that there exist similar trends in these two stars, caused by systematic errors. 
%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
}
\end{figure}

The third general idea is that we need to control for over-fitting.
That is, once you have a flexible-enough model you can in principle fit \emph{anything},
  whether it was caused by the spacecraft, intrinsic stellar variability, or a transiting exoplanet.
How do you prevent a very flexible model from taking small noise-induced fluctuations in all the input data
  and carefully combining them linearly into detailed models for every nook and cranny in the target data?
In most projects in astrophysics, over-fitting is controlled for by limiting model freedom.
The model is restricted in the number of parameters
  (as in ``you can't have more parameters than data points'')
  or by limiting the dimensionality
  (as in principal components analysis)
  or by applying strong priors
  (as with smoothness priors or regularization, 
  that effectively reduce freedom without explicitly reducing the number of parameters).
In each case, the restriction on model freedom is controlled by some \emph{hyper-parameter}
  (such as the number of inputs, or number of principal components, or the strength of the smoothness prior).
The hyper-parameters can be set or tested with tools like cross-validation,
  the fully marginalized likelihood (Bayes factor or evidence),
  chi-squared statistical criteria,
  or intuition or heuristics.
Here we take a different and more general approach, which is to use a train-and-test framework.

@@

Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
  that any particular data-driven model is better or worse than any other.
This problem is a problem for \name, and for the \Kepler\ PDC, and any other data-driven calibration models.
One might think that the ``best'' model is the one that predicts data with lowest variance;
  this would be true if all models adhered to the same train-and-test framework, which they don't.
Besides, a model that can predict not just the spacecraft-induced variability,
  but also variability caused by exoplanet transits of interest,
  will effectively over-fit and distort the most important information in the light-curves.
That is, what is considered best for modelling the data depends on the objectives of the user.
For us, who are interested (in the long term) in finding and characterizing Earth analogs,
  the ``best'' data-driven model is the one that produces the most success in finding and characterizing Earth analogs!
What we will show in what follows is that the \name\ photometry does not distort
  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data.
  and promising properties of the \name\ outputs.
In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.

We also want to emphasis that all the calibration in this paper for \Kepler is 
  based on the assumption that the device is 'self-calibratable', 
  which means all the information we need to calibrate the device are contained in the device itself 
  (either in science data or engineering data) and no external information, 
  for example, measurements from other device, are needed.
  And a description of the method in the machine learning context can be found in \cite{icml}

\section{\name\ specification and hyper-parameters}
\subsection{\name\ model}
Each individual \Kepler\ target star is, for each quarter (each 90-ish-day period)
  on a particular CCD on the \Kepler\ focal plane.
Associated with each target star is some set of pixels,
  located in a small contiguous patch more-or-less centered on the target star,
  and telemetered down once for every 30-min exposure.
(Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.)
That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.

>>>>

\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[normalem]{ulem}
%\usepackage{caption} 
%\usepackage{subcaption} 
\usepackage{epstopdf}
\usepackage{color}
\usepackage{hyperref}
\usepackage{url}

@@

%\graphicspath{{figures/png/}}

\newcommand{\notenglish}[1]{\textit{#1}}
\newcommand{\sic}{\notenglish{sic}}
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\Kepler}{\project{Kepler}}
\newcommand{\name}{CPM}
\newcommand{\set}[1]{\mathcal{#1}}
\newcommand{\given}{\,|\,}
\newcommand{\todo}[1]{\textbf{#1}}
\newcommand{\revise}[1]{\textcolor{green}{#1}}
\newcommand{\remove}[1]{\sout{#1}}

@@

\title{ \remove{Calibrating the pixel-level Kepler imaging data with a causal data-driven model\\}
  \revise{
  A Causal, Data-Driven Approach to Modeling the Kepler Image Data
 \\ }
}
\author{%
  Dun~Wang\altaffilmark{\ref{CCPP}},
  David~W.~Hogg\altaffilmark{\ref{CCPP},\ref{CDS},\ref{MPIA},\ref{email}},
  Daniel~Foreman-Mackey\altaffilmark{\ref{UW},\ref{SF}},
  Bernhard~Sch\"olkopf\altaffilmark{\ref{MPIIS}}
  }
\newcounter{address}
\setcounter{address}{1}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CCPP}%
  Center for Cosmology and Particle Physics, Department of Physics, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{CDS}%
  Center for Data Science, New York University}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIA}%
  Max-Planck-Institut f\"ur Astronomie, Heidelberg, Germany}
\altaffiltext{\theaddress}{\stepcounter{address}\label{email}%
  To whom correspondence should be addressed; \texttt{<david.hogg@nyu.edu>}.}
\altaffiltext{\theaddress}{\stepcounter{address}\label{MPIIS}%
  Max-Planck-Institut f\"ur Intelligente Systeme, T\"ubingen}
\altaffiltext{\theaddress}{\stepcounter{address}\label{UW}%
 Astronomy Department, University of Washington, Seattle, WA 98195}
\altaffiltext{\theaddress}{\stepcounter{address}\label{SF}%
Sagan Fellow}

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
the most precise photometric measurements of stars ever made---%
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level so that
it can capture very fine-grained information about the variation of the spacecraft.
\remove{The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star.} \revise{The CPM models the systematic effects in the time series of a pixel using the pixels
around many other stars and the assumption that any shared signal in
these causally disconnected light curves is caused by instrumental
effects.} In addition, we use the target star's future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four \remove{hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components),}
\revise{tuning parameters---the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components,}
 which we set by cross-validation. 
We determine a generic set of \remove{hyper-parameters}\revise{tuning parameters} that works well for most of the stars and apply the method to a corresponding set of target stars.
\remove{We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.} 
\revise{We find that \name\ can consistently produce relatively low-noise (CDPP) light-curves. In this paper, we demonstrate that pixel-level de-trending is possible while retaining transit signals (with a train-and-test framework) and we think that methods like \name\ is generally applicable and might be useful for  K2, TESS, etc, where the data aren't these clean postage stamps like \Kepler.}

@@

\section{Introduction}

The photometric measurements of stars made by the \Kepler\ \remove{satellite}\revise{space craft} are precise enough
  to permit discovery of exoplanet transits with depths smaller than $10^{-4}$.
This precision results from great spacecraft stability,
  supplemented by various methods for removing small residual spacecraft-induced and stellar-variability trends in the brightnesses,
  either filtering the data (with things like median filters)
  or fitting the data with flexible models (like polynomials or splines or Gaussian Processes; 
  \cite{gaussian}).
When employed in the service of exoplanet search and characterization,
  these methods are usually agnostic about whether photometric variations originate in the spacecraft or in the star itself;
  that is, they obliterate intrinsic stellar variability along with spacecraft issues.

In general, there are many reasons for apparent photometric variability in a \Kepler\ source.
There is intrinsic stellar variability,
  which is of interest to some and a nuisance to others.
There is also variability of overlapping fainter stars;
  that is, confusion noise combined with variability of the confusing sources.
There are small changes in spacecraft pointing,
  which leads to slightly different illumination of the focal-plane pixels,
  and thus different sensitivity to variations in the device.
There are also \emph{intra-pixel} sensitivity variations that can contribute, which was first measured by \revise{\cite{subpixel}}.
There are small changes in spacecraft temperature,
  which lead to point-spread function (PSF) and differential \remove{(across the focal plane)} pointing changes.
These also lead to changes in pixel and intra-pixel illumination.
Stellar proper motion, geometric parallaxes, and differential stellar aberration as the spacecraft orbits all do more of the same.
There is electronic cross-talk between detectors and charge-transfer inefficiency;
  these can effectively transfer variability from one source to another.
There are additional electronics effects like ``rolling bands'' that put additional features into light-curves \revise{\citep{handbook}}.
There are also \remove{probably} changes to the detector sensitivity with temperature and time,
  possibly illimunation-history effects,
  and possibly sources of variability not yet considered.
The remarkable thing about \Kepler\ is that it is trying to measure stars at a level of precision
  much higher than ever previously attempted;
  new effects really \emph{must} appear at some point.
In \figurename~\ref{ccd}, we show the pixel-level variability in the \Kepler\ data
  near one bright star that shows minimal intrinsic variability;
  this figure highlights the spacecraft-induced effects.

\remove{We propose and advise dealing with}\revise{We propose to deal with} these variations in \Kepler\ light-curves by \emph{modeling} them.
In this context, a model is \remove{(at least)} a parameterized function that can predict data, given parameter settings,
  and an objective function that can be used to set or sample those parameters.
In some cases, the objective function can be given a probabilistic justification or interpretation, e.g., if it is constructed using a likelihood and a prior pdf.
The model can be a physical model (of the spacecraft PSF, pointing, temperature, and so on)
  or it can be a flexible, effective model that has no direct interpretation in terms of physical spacecraft parameters.
If done well, we would expect a physical model to do a better job,
  because it embodies more prior information,
  but it requires research and intuition about dominant effects. 
If this research and intuition is wrong or incomplete, a physical model may actually perform worse.
The model we propose here is in the non-physical, effective category.
The \Kepler\ community is familiar with these kinds of models;
  to our knowledge, \emph{all} successful light-curve ``de-trending'' methods
  are flexible, effective models.

One such method---one that is designed to describe or model spacecraft-induced problems
  but \emph{not} interfere with measurements of stellar variability---%
  is the \Kepler\ Presearch \remove{(\sic)} Data Conditioning (PDC, \cite{pdc1}).
The PDC builds on the idea that systematic errors have a temporal structure that can be extracted from ancillary quantities. 
%This seems the original paper on PDC:
%[PDC1] https://kepler.nasa.gov/science/ForScientists/papersAndDocumentation/SOCpapers/7740-67-pdc-jtwicken-copyright.pdf
%
%This describes the later version of PDC:
%[PDC2] http://arxiv.org/pdf/1203.1382v1.pdf
%[PDC3] http://arxiv.org/pdf/1203.1383v1.pdf

In the first PDC \citep{pdc1}, 
  removal of systematic errors was performed based on correlations with a set of ancillary engineering data. 
These data include the temperatures at the local detector electronics below the CCD array, 
  and polynomials describing the centroid motion of the targets from PA\revise{(Photometric Analysis)}.

In \cite{pdc2,pdc3}\remove{, filtered light-curves of other stars are used instead. 
The light-curve of a target star is projected on the leading eight principal components of these light-curves. 
This projection is then removed from the star's light-curve. 
The principal components are computed from a set of relatively quiet stars close in position and magnitude. 
This was done since it was observed that otherwise, too much of the stellar variability was being removed.}

\revise{In the most recent version of PDC (PDC-MAP, \cite{pdc2,pdc3}), filtered light-curves of other stars are used
instead. Using a set of relatively quiet stars on each detector, the
top 8 principle components are computed for every quarter of Kepler
data. The maximum a posteriori linear combination of these basis light
curves---computed using an empirical prior on the trend
magnitudes---are used to model and remove the systematics in all the
Kepler light curves. The choice to use such a small number of
components and to apply priors was made in order to reduce
over-fitting and retain physical signals after systematics removal.}

\remove{From the point of view of the present paper, 
one can only guarantee that {\em no} stellar variability is removed if the stars do not depend on time at all.
If both the target star signal as well as some of the other stars do depend on time, 
  then time acts as a confounder influencing both, and thus the true signals are not statistically independent, 
  and thus the target signal may be compromised. 
We suspect that this effect is limited in} \cite{pdc2,pdc3}, 
  \remove{since only eight principal components are used, which limits the capacity of the model.}

PDC \remove{``de-trends''}\revise{"co-trends" or calibrates} the \Kepler\ light-curves by removing those parts that are explained by the basis light-curves
  generated from a principal components analysis (PCA) of filtered light-curves.
That is, it exploits statistical dependences between different time series, regularizing the fit (and avoiding over-fitting) 
  by filtering and restricting the dimensionality (through PCA).

The method proposed here, \name, shares the motivation of PDC.
The main differences are that
\begin{enumerate}
\item
\name\ works in the pixel domain, not the light-curve domain, so it has access to more fine-grained information
\item
\name\ has far more freedom (far more parameters) than the PDC
  but it strictly avoids over-fitting the light-curves on exoplanet-transit time-scales
  through strong regularization and a train-and-test framework. 
  \revise{PDC mitigates overfitting by
reducing the freedom of the model and applying empirical priors to the
fit coefficients.}
\item 
\name\ directly optimizes for prediction accuracy, while PDC uses PCA projections.
\item
\remove{the purpose of \name\ is to search for exoplanets, so in \name, intrinsic stellar
  variability is also removed as well as the systematics.}
  \revise{The current version of \name\ is
tuned to remove systematics while minimizing the impact on exoplanet
transit signals. It makes no attempt to retain lower frequency signals
that can be produced by other astrophysical signals.}
\item 
\name\ uses as inputs only instantaneous values of other stars, plus near future and past of the star itself in an autoregressive fashion, while PDC works with time series (light-curves) of the other stars.
\end{enumerate}

The two methods (\name\ and PDC) are similar however,
  in that they both make the \remove{(implicit or explicit)} assumption that whatever spacecraft effects are imprinting variability on a stellar light-curve
  must also be imprinting similar or related variability on other light-curves.
\remove{In their current versions, they also assume that the relationships can be captured with linear models (although we have also used nonlinear predictions methods for \name, which would be harder to do in PDC).}
By going to the pixel level (unlike the PDC, which works at the photometry level),
  \name\ makes it easier for the model to capture variability
  that is coming through variations in the centroids and point-spread function
  from spacecraft pointing, roll, and temperature.

Before we start, a few reminders about the \Kepler\ data are in order:
The \remove{satellite}\revise{space craft} \remove{always observes}\revise{observed} precisely the same field, at fixed pointing (as closely as possible).
\revise{About 6\% of the 96,465,600 pixels}\remove{Only a few percent of the 80 million pixels} in the focal plane are telemetered down
  to Earth from each 30-min exposure;
  the telemetered pixels are associated with \Kepler\ target stars chosen for study by the \Kepler\ Team \revise{(along with a non-trivial set collateral pixels used for calibration)}.
The \remove{satellite}\revise{space craft} is rolled by 90~deg every \remove{90-ish}\revise{93} days (to satisfy Solar-Angle constraints).
The focal plane contains many CCDs;
  this plus the 90-deg rotations means that each star is at a particular location
  on a particular CCD for \remove{90-ish-day}\revise{quarter} contiguous periods of time.
The PSF varies strongly across the field and is badly sampled.
The stars span a huge range in brightness;
  some of \Kepler's most important targets even saturate the device and bleed charge.
The stellar photometry returned by the \Kepler\ SAP and PDC pipelines is based on
  straight, \emph{unweighted} sums of pixels in small patches centered on the stellar centroid.
We will return to this latter point at the end;
  this kind of photometry cannot be optimal;
  it must be possible to do a better job with the photometric measurements.
That's beyond the scope of this project but a place for a valuable intervention on the \Kepler\ data.

\remove{The scope of this project is an intervention---\name---that makes the \Kepler\ transit photometry more precise.}

We describe the method and deliver all the relevant code in a public, open-source repository.
We also provide an interface to the \Kepler\ data that \remove{delivers improved ``\name\ photometry''}\revise{can be used
to produce ''\name\ photometry''}
  for every \Kepler\ target.

@@

The second general idea about data-driven modelling is the investigator's beliefs about the causal processes that generate the data are crucial in restricting the kinds of data that can be used as input to the model.
That is, different assumptions about the physical properties of the data and the data-taking system lead to different structures for the data-driven model.
In the case of \Kepler\ data, 
  if we examine two arbitrary stars far away from each other 
  on the same CCD as in Fig~\ref{ccd} (every grid in the plot is a pixel light-curve time series), 
  we can obviously see that the two stars that are hundreds pixel away from each other do have similar trends. 
  If we believe that different stars in the \Kepler\ field vary independently 
  (that is, are not physically synchronized in any way) because of the distance between them, 
  then the only reason that one star might show variability that is strongly \emph{predictive} (useful for prediction) of another star's variability
  is that both stars are being observed by the same device or spacecraft.
That is, one star's pixels can be used to predict another star's pixels inasmuch as spacecraft issues imprint on both stars in related ways;
  they share a common cause---the systematics.  
For another example, if we think the spacecraft is being affected by
  processes that take place over time-scales longer than a single read-out
  (for example, thermal processes),
  then it would be sensible to model the data at time $t$ using not just simultaneous data, but also data from a range of times around $t$.
For another example, if an investigator doesn't care about preserving stellar variability,
  and just wants to detect exoplanet transits (say),
  pixels from the target star can be used to predict pixels from the target star,
  provided they are at large-enough time lags that they don't contain information about
  the signals of interest (i.e., the transits).
That is, if the model is designed to fit not just spacecraft variability
  but also intrinsic stellar variability,
  the predictive model will be permitted to use as input pixels that \emph{do} overlap the target star.
In what follows, we are going to use input data both from pixels of other stars and the target star pixels' past and future.
These models ought to remove both spacecraft variability and intrinsic stellar variability, which is \remove{optimal}\revise{optimized} for exoplanet transit searching.

\begin{figure}[p]
\begin{center}
\includegraphics[width=0.4\textwidth]{f1a}
\includegraphics[width=0.4\textwidth]{f1b}
\end{center}
\caption{
  \label{ccd} 
  Stars on the same CCD share systematic errors. 
  The two panels show pixel fluxes (brightnesses) for two stars in quarter 5. \emph{Left:} KIC 5088536, \emph{Right:} KIC 5949551; 
  here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
  but far enough apart such that there is no stray light from one affecting the other. 
  Each panel shows the pixels contributing to the respective star.
  Note that there exist similar trends in these two stars, caused by systematic errors. 
%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
}
\end{figure}

The third general idea is that we need to control for over-fitting.
That is, once you have a flexible-enough model you can in principle fit \emph{anything},
  whether it was caused by the spacecraft, intrinsic stellar variability, or a transiting exoplanet.
How do you prevent a very flexible model from taking small noise-induced fluctuations in all the input data
  and carefully combining them linearly into detailed models for every nook and cranny in the target data?
In most projects in astrophysics, over-fitting is controlled for by limiting model freedom.
The model is restricted in the number of parameters
  (as in ``you can't have more parameters than data points'')
  or by limiting the dimensionality
  (as in principal components analysis)
  or by applying strong priors
  (as with smoothness priors or regularization, 
  that effectively reduce freedom without explicitly reducing the number of parameters).
In each case, the restriction on model freedom is controlled by some \emph{\remove{hyper-parameter}\revise{tuning parameters}}
  (such as the number of inputs, or number of principal components, or the strength of the smoothness prior).
The \remove{hyper-parameters}\revise{tuning parameters} can be set or tested with tools like cross-validation,
  the fully marginalized likelihood (Bayes factor or evidence),
  chi-squared statistical criteria,
  or intuition or heuristics.
Here we take a different and more general approach, which is to use a train-and-test framework.

@@

Finally, the fifth general idea is that there is no objective \emph{ground truth} against which we can tell
  that any particular data-driven model is better or worse than any other.
This problem is a problem for \name, and for the \Kepler\ PDC, and any other data-driven calibration models.
One might think that the ``best'' model is the one that predicts data with lowest variance;
  this would be true if all models adhered to the same train-and-test framework, which they don't.
Besides, a model that can predict not just the spacecraft-induced variability,
  but also variability caused by exoplanet transits of interest,
  will effectively over-fit and distort the most important information in the light-curves.
That is, what is considered best for modelling the data depends on the objectives of the user.
For us, who are interested (in the long term) in finding and characterizing Earth analogs,
  the ``best'' data-driven model is the one that produces the most success in finding and characterizing Earth analogs!
What we will show in what follows is that the \name\ photometry does not distort
  artificial exoplanet transit signals injected into real \Kepler\ pixel-level data
  and promising properties of the \name\ outputs \revise{on real Kepler light-curves}.
In the end, the value of the \name\ will be demonstrated by the scientific projects it enables.

We also want to emphasis that all the calibration in this paper for \Kepler is 
  based on the assumption that the device is \remove{'self-calibratable'}\revise{can be self-calibrated}, 
  which means all the information we need to calibrate the device are contained in the device itself 
  (either in science data or engineering data) and no external information, 
  for example, measurements from other device, are needed.
  And a description of the method in the machine learning context can be found in \cite{icml2015}

\section{\name\ specification and \revise{tuning parameters}}
\subsection{\name\ model}
Each individual \Kepler\ target star is, for each quarter (each \remove{90-ish-day})
  on a particular CCD on the \Kepler\ focal plane.
Associated with each target star is some set of pixels,
  located in a small contiguous patch \remove{more-or-less} centered on the target star,
  and telemetered down once for every 30-min exposure.
Here we are ignoring all short-cadence data that is taken in a different mode with shorter exposures.
That is, each telemetered pixel in each CCD is associated with a particular \Kepler\ target star.
